### 2015-10-14 paper.tex
Add CFT to abstract
Properties --> flow
Minor introduction edit

The mechanical power, total rotor drag, and near-wake properties of a 1:6 scale
Reference Model 2 (RM2) were measured in a towing tank. Performance was measured
at multiple Reynolds numbers by varying tow carriage speed, and weak linear
$Re$-dependence was achieved at a turbine diameter Reynolds number $Re_D \approx
10^6$. An optimal tip speed ratio $\lambda_0 = 3.1$ was chosen, at which the
near wake velocity was measured at 1 m $(x/D=0.93)$ downstream. Mean velocity,
turbulence, and mean kinetic energy transport mechanisms were compared and
contrasted with results from a high solidity turbine acquired with the same test
apparatus. Overall, lower levels of streamwise wake recovery were calculated for
the RM2 rotor---a consequence of both the relatively low solidity and tapered
blades. The effects of blade support strut drag on turbine performance were
investigated by covering the rotor's NACA 0021 struts with cylinders. As
expected, this modification drastically reduced rotor power coefficient. Strut
drag was also measured for the NACA 0021 and cylindrical configurations with the
blades removed. These measurements provide a comprehensive open dataset for
validating numerical models' predictive capabilities for low solidity rotors.

@@

Sandia National Laboratories, in collaboration with the US Department of Energy
developed the Reference Model devices to provide modeling targets for advancing
marine hydrokinetic (MHK) energy technology \cite{Neary2014}. The Reference
Model 2 (RM2), a cross-flow turbine intended for river environments, was
initially designed by Barone et al. \cite{Barone2011} using the CACTUS vortex
line code \cite{Murray2011}. A scaled physical model of the RM2 was then
designed and built by the Saint Anthony Falls Laboratory (SAFL) to validate the
CACTUS predictions. Experimental performance measurements were significantly
lower than the numerical results \cite{Hill2014}, which was assumed to be caused
by the physical model's low Reynolds number
\begin{equation}
Re_L = \frac{UL}{\nu},
\label{eq:Re}
\end{equation}
where $U$ and $L$ are characteristic length scales, and $\nu$ is the fluid
kinematic viscosity.

>>>>

The mechanical power, total rotor drag, and near-wake flow of a 1:6 scale
Reference Model 2 (RM2) cross-flow turbine were measured in a towing tank.
Performance was measured at multiple Reynolds numbers by varying tow carriage
speed, and weak linear $Re$-dependence was achieved at a turbine diameter
Reynolds number $Re_D \approx 10^6$. An optimal tip speed ratio $\lambda_0 =
3.1$ was chosen, at which the near wake velocity was measured at 1 m
$(x/D=0.93)$ downstream. Mean velocity, turbulence, and mean kinetic energy
transport mechanisms were compared and contrasted with results from a high
solidity turbine acquired with the same test apparatus. Overall, lower levels of
streamwise wake recovery were calculated for the RM2 rotor---a consequence of
both the relatively low solidity and tapered blades. The effects of blade
support strut drag on turbine performance were investigated by covering the
rotor's NACA 0021 struts with cylinders. As expected, this modification
drastically reduced rotor power coefficient. Strut drag was also measured for
the NACA 0021 and cylindrical configurations with the blades removed. These
measurements provide a comprehensive open dataset for validating numerical
models' predictive capabilities for low solidity rotors.

@@

Sandia National Laboratories, in collaboration with the US Department of Energy
developed the Reference Model devices to provide modeling targets for advancing
marine hydrokinetic (MHK) energy technology \cite{Neary2014}. The Reference
Model 2 (RM2), a cross-flow turbine intended for river environments, was
initially designed by Barone et al. \cite{Barone2011} using the CACTUS vortex
line code \cite{Murray2011}. A scaled physical model of the RM2 was then
designed and built by the Saint Anthony Falls Laboratory (SAFL) to validate the
CACTUS predictions. Experimental performance measurements were significantly
lower than the numerical results \cite{Hill2014}, which was assumed to be a 
result of the physical model's low Reynolds number
\begin{equation}
Re_L = \frac{UL}{\nu},
\label{eq:Re}
\end{equation}
where $U$ and $L$ are characteristic length scales, and $\nu$ is the fluid
kinematic viscosity.
